A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-29 main.tex
Writing on \LTP.

\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}
\subsection{\LMD}

>>>>

\section{Informal Overview of \LMD}

In this section, we check \LMD informally after checking \LTP and \LLF which are the basis of \LMD.

\subsection{\LTP}

% quote and unquote

In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.

% transition variable

The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
It is used to show the thickness of quoting.
For example, $\TB_\alpha 1$ is a fragment of code which becomes $1$ after run it once and
$\TB_\alpha \TB_\beta 1$ becomes $1$ after run it twice.

% transition

A sequence of transition variables is a transition which is called a stage in \LMD.
In \LTP, all judgement has a transition.
Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.

% transition abstraction

There are abstraction for transition variables and application for transition abstraction in \LTP.
They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.

% transition application

% run

% CSP

% omitting residualization

\subsection{\LLF}
\subsection{\LMD}
